\documentclass[10pt, aspectratio=43,leqno]{beamer}
\usepackage{presentation}
\usetheme{Boadilla}
\setbeamersize
{
  text margin left=1in,
  text margin right=1in
}
\usepackage{mathtools}
\usepackage{enumerate}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{fontawesome}
\setlength{\parskip}{6pt}

\newtheorem{proposition}[theorem]{Proposition}

\newcommand{\R}{\ensuremath{\mathbb{R}}}
\newcommand{\Q}{\ensuremath{\mathbb{Q}}}
\newcommand{\N}{\ensuremath{\mathbb{N}}}
\newcommand{\B}{\ensuremath{\mathcal{B}}}
\newcommand{\X}{\ensuremath{\mathcal{X}}}

\title{\textsc{Infinity}}
\subtitle{The Mathematics Club}
\author{IISER Mohali}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}
  \textsc{Ronald Huidrom}, Mathematics Major (4th year) \\
  {\color{blue} Convener} \\
  \vspace*{.5cm}
  
  \textsc{Joshua Abraham}, Mathematics Major (3rd year) \\
  {\color{blue} Co-convener} \\
\end{frame}

\begin{frame}
  \frametitle{The Vision of Infinity}
  Mathematics is fun --- and it's more fun when we do it together. The club welcomes everyone on board and spreads the joy of doing mathematics. \\
\end{frame}

\begin{frame}
  \frametitle{Who is Infinity for?}
  \pause
  Infinity is for everyone. \pause \\
  \vspace*{.5cm}
  More precisely, Infinity is for people who love creating and solving logic puzzles, riddles, games, codes and such. \pause\\
  \vspace*{.5cm}
  Even if you think you are \emph{not} good at mathematics, there is always something you can do in the club and enjoy.
\end{frame}

\begin{frame}
  \frametitle{Club Activities}
  \framesubtitle{The Cool Stuff for Everyone}
  \pause
\begin{enumerate}
\item\label{item:1} Hackathons 
\begin{itemize}
\item\label{item:2} Teams work together on a set of puzzles, games, math problems within a time limit.
\end{itemize}
\pause
\item\label{item:3} Code Breaking 
\begin{itemize}
\item Both teams and individual.
\end{itemize}
\pause
\item\label{item:4} Game Nights 
\begin{itemize}
\item Solve puzzles, games from combinatorial game theory, game on graphs and more.
\end{itemize}
\pause 
\item\label{item:5} Magic Showcase 
\begin{itemize}
\item People showing off their magic skills, like card tricks.
\end{itemize}
\end{enumerate}
\end{frame}

\begin{frame}
  \frametitle{Club Activities}
  \framesubtitle{The Nerdy \& Geeky Stuffs for People Who Actually Love Mathematics}
  \pause
\begin{enumerate}
\item\label{item:6} Talk Series
\begin{itemize}
\item Talks by math majors/PhDs/professors on various topics such as their summer internships/thesis/research or just fun things.
\end{itemize}
\pause 
\item\label{item:7} Special Groups
\begin{itemize}
\item We are planning on creating and supporting student groups for learning different fields of math like computational math group, geometry and topology group... etc.
\end{itemize}
\end{enumerate}
\end{frame}

\begin{frame}
  \frametitle{Upcoming Events}
  \pause
\begin{enumerate}
\item\label{item:8} Hackathon: Infinity War 
\begin{itemize}
\item Expected time: mid-November 
\item Teams of four: one math/physics major, three ms21/ms22 students
\item You brainstorm and solve puzzles, games, problems within a time limit.
\end{itemize}
\pause
\item\label{item:9} Battle Royal: Code Breaking 
\begin{itemize} 
\item Expected time: early-January
\item Individually compete.
\end{itemize}
\end{enumerate}
\end{frame}

\begin{frame}
  We are looking forward to interacting with you all.
\end{frame}

\end{document}